A Rough Guide to Pre-processing High-Frequency Animal Tracking Data

### 2020-10-09 05_calibration_data.Rmd
remove filter NBS, prep for recurse

```{r}
# plot data
fig_data_bbox <-
  ggplot()+
  geom_path(data = data_raw,
            aes(x, y),
             col = "grey", alpha = 0.5, size = 0.3)+
  geom_point(data = data_raw,
             aes(x, y,
                 col = x > 645000),
             alpha = ifelse(data_raw$x > 645000, 0.5, 1),
             size = ifelse(data_raw$x > 645000, 0.3, 2),
             show.legend = F)+
  scale_color_brewer(palette = "Set1")+
  geom_vline(xintercept = 645000,
             col = "grey", lty = 2)+
  ggspatial::annotation_scale(location = "br")+
  ggthemes::theme_map()+
  coord_sf(crs = 32631)

@@

### Remove low base station positions

```{r}
# save a copy
data_unproc <- copy(data)

# remove NBS <= 3
data <- atl_filter_covariates(data = data,
                              filters = "NBS > 3")
```

```{r}
fig_low_nbs <-
  ggplot()+
  geom_path(data = data,
            aes(x, y),
             col = "grey", alpha = 0.5, size = 0.3)+
  geom_point(data = data_unproc,
            aes(x, y,
                col = as.factor(NBS > 3)),
            shape = 1,
            alpha = 0.5, size = 0.3, show.legend = F)+
  scale_color_brewer(palette = "Set1")+
  ggthemes::theme_map()+
  ggspatial::annotation_scale(location = "tl")+
  coord_sf(crs = 32631)+
  labs(colour = "NBS")

# save figure
ggsave(fig_low_nbs, filename = "figures/fig_low_nbs.png",
       width = 185 / 25, height = 185 / 25)
```

@@

```{r}
# plot filtered data
fig_speed_outliers <-
  ggplot()+
  geom_path(data = data,
            aes(x, y),
             col = "grey", alpha = 0.5, size = 0.3)+
  geom_point(data = data,
             aes(x, y, 
                 col = speed_in < 15.7),
             size = 0.3, alpha = 0.5,
             show.legend = F)+
  scale_color_brewer(palette = "Set1")+
  ggthemes::theme_map()+
  ggspatial::annotation_scale(location = "tl")+
  coord_sf(crs = 32631)+
  labs(colour = "speed (m/s)")

@@

```{r}
# make figure
fig_smooth <-
  ggplot()+
  geom_path(data = data,
             aes(x, y),
            col = RColorBrewer::brewer.pal(4, "Set1")[4])+
  annotate(geom = "rect",
           xmin = c(650785, 650045),
           ymin = c(5904450, 5902700),
           xmax = c(652500, 650682),
           ymax = c(5906133, 5903080),
           fill = "grey90",
           alpha = 0.5,
           col = NA)+
    annotate(geom = "text",
           x = c(650785, 650045) + 400,
           y = c(5904450, 5902700) + 300,
           col = "black",
           label = c("d", "e"))+
  theme_void()+
  coord_sf(crs = 32631)+
  labs(colour = "track")

# make zoomed in figures
fig_inset <- mapply(function(xl, yl) {
  ggplot()+
    geom_point(data = data_raw[!data_unproc, on = c("x", "y")],
               aes(x, y),
               col = "grey",
               shape = 4,
               size = 0.4)+
    geom_point(data = data_unproc,
               aes(x, y),
               col = RColorBrewer::brewer.pal(3, "Set1")[3],
               shape = 1, 
               alpha = 0.5)+
    geom_path(data = data,
              aes(x, y),
              col = RColorBrewer::brewer.pal(4, "Set1")[4])+
    ggthemes::theme_few()+
    theme(axis.title = element_blank(),
          axis.text = element_blank())+
    ggspatial::annotation_scale(location = "br")+
    coord_cartesian(
             xlim = xl,
             ylim = yl, expand = F
             )+
    labs(colour = "track")
}, list(xl1 = c(650785, 652500),
        xl2 = c(650045, 650682)),
   list(yl1 = c(5904450, 5906133),
        yl2 = c(5902700, 5903080)),
SIMPLIFY = FALSE)

# add global figure to second inset
fig_inset[[2]] <- fig_inset[[2]] +
  annotation_custom(grob = ggplotGrob(fig_smooth),
                    xmin = 649990,
                    xmax = 650045 + (650682 - 650045)/2,
                    ymin = 5903080 - (5903080 - 5902700)/2.5,
                    ymax = 5903080
                    )

fig_median_smooth <- 
  wrap_plots(fig_inset)+
  plot_annotation(tag_levels = "a",
                  tag_prefix = "(",
                  tag_suffix = ")")
# save figure
ggsave(filename = "figures/fig_calib_median_smooth.png",
       width = 185 / 25, height = 90 / 25)
```

@@

```{r}
# make combined walkthrough figure
figure_walkthrough <- 
  wrap_plots(
  append(
    list(
      fig_data_bbox, fig_low_nbs, fig_speed_outliers), 
    fig_inset),
design = "ABD\nACE")+
  plot_annotation(tag_levels = "a",
                  tag_prefix = "(",
                  tag_suffix = ")")

# save combined figure
ggsave(figure_walkthrough,
       filename = "figures/fig_walkthrough.png",
       height = 130, width = 225, units = "mm")
```

@@

# get recurse data for a 10m radius
data_recurse <- getRecursions(data_unproc[, list(x, y, time, TAG)],
                              radius = 200)
```

>>>>

```{r}
# plot data
fig_data_bbox <-
  ggplot()+
  geom_path(data = data_raw,
            aes(x, y),
             col = "grey", alpha = 0.5, size = 0.3)+
  geom_point(data = data_raw,
             aes(x, y,
                 col = x > 645000),
             alpha = ifelse(data_raw$x > 645000, 0.5, 1),
             size = ifelse(data_raw$x > 645000, 0.3, 2),
             show.legend = F)+
  scale_colour_manual(values = c("grey", pal[3]))+
  geom_vline(xintercept = 645000,
             col = "grey", lty = 2)+
  ggspatial::annotation_scale(location = "br")+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank(),
        panel.background = element_rect(fill = "grey99"))+
  coord_sf(crs = 32631)

@@

@@

```{r}
# plot filtered data
fig_speed_outliers <-
  ggplot()+
  geom_point(data = data,
             aes(x, y, 
                 col = speed_in < 24),
             size = 0.3, alpha = 0.5,
             show.legend = F)+
  scale_color_manual(values = c("grey", pal[3]))+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank(),
        panel.background = element_rect(fill = "grey99"))+
  ggspatial::annotation_scale(location = "tl")+
  coord_sf(crs = 32631)+
  labs(colour = "speed (m/s)")

@@

```{r}
# make figure
# fig_smooth <-
#   ggplot()+
#   geom_path(data = data,
#              aes(x, y),
#             col = RColorBrewer::brewer.pal(4, "Set1")[4])+
#   annotate(geom = "rect",
#            xmin = c(650785, 650045),
#            ymin = c(5904450, 5902700),
#            xmax = c(652500, 650682),
#            ymax = c(5906133, 5903080),
#            fill = "grey90",
#            alpha = 0.5,
#            col = NA)+
#     annotate(geom = "text",
#            x = c(650785, 650045) + 400,
#            y = c(5904450, 5902700) + 300,
#            col = "black",
#            label = c("d", "e"))+
#   theme_void()+
#   coord_sf(crs = 32631)+
#   labs(colour = "track")

# make zoomed in figures
fig_inset <- mapply(function(xl, yl) {
  ggplot()+
    geom_point(data = data_raw[!data_unproc, on = c("x", "y")],
               aes(x, y),
               col = "grey",
               shape = 4,
               size = 0.4)+
    geom_point(data = data_unproc,
               aes(x, y),
               col = pal[3],
               shape = 19, 
               alpha = 0.5)+
    geom_path(data = data,
              aes(x, y),
              col = RColorBrewer::brewer.pal(4, "Set1")[4])+
    ggthemes::theme_few()+
    theme(axis.title = element_blank(),
          axis.text = element_blank())+
    ggspatial::annotation_scale(location = "br")+
    coord_cartesian(
             xlim = xl,
             ylim = yl, expand = F
             )+
    labs(colour = "track")
}, list(xl1 = c(650785, 653250),
        xl2 = c(650045, 650682)),
   list(yl1 = c(5904450, 5906133),
        yl2 = c(5902700, 5903080)),
SIMPLIFY = FALSE)

# # add global figure to second inset
# fig_inset[[2]] <- fig_inset[[2]] +
#   annotation_custom(grob = ggplotGrob(fig_smooth),
#                     xmin = 649990,
#                     xmax = 650045 + (650682 - 650045)/2,
#                     ymin = 5903080 - (5903080 - 5902700)/2.5,
#                     ymax = 5903080
#                     )

fig_median_smooth <- fig_inset[[1]]
  # wrap_plots(fig_inset)+
  # plot_annotation(tag_levels = "a",
  #                 tag_prefix = "(",
  #                 tag_suffix = ")")
# save figure
ggsave(fig_median_smooth,
       filename = "figures/fig_calib_median_smooth.png",
       width = 90 / 25, height = 90 / 25)
```

@@

```{r}
# make combined walkthrough figure
figure_walkthrough <-
wrap_plots(
  list(
    fig_data_bbox, fig_speed_outliers, fig_median_smooth),
  design = "AB\nAC")+
  plot_annotation(tag_levels = "a",
                  tag_prefix = "(",
                  tag_suffix = ")")

# save combined figure
ggsave(figure_walkthrough,
       filename = "figures/fig_walkthrough.png",
       height = 130, width = 170, units = "mm")
```

@@

# get recurse data for a 10m radius
data_recurse <- getRecursions(data_unproc[, list(x, y, time, TAG)],
                              radius = 100)
```
